Why Real-World Subgraph Isomorphism is Easy, \\ and What This Means for Graph Databases

### 2016-10-07 paper/paper.tex
Plot better

% \usepackage{showframe}

@@

\begin{figure}[p]
    \centering\includegraphics{gen-graph-induced.pdf}
    \caption{Behaviour of algorithms on the induced variant, shown in the style
    of \cref{figure:non-induced}. The fifth row plots constrainedness: the darkest region is where
    $\kappa = 1$, and the lighter regions show where the problem is either over-
    or under-constrained. The final row shows when the Glasgow algorithm performs better when given
    the complements of the pattern and target graphs as inputs---the solid lines show the location
of the phase transition, and the dotted lines are $t_d=0.5$ and the $p_d=t_d$ diagonal.}\label{figure:induced}
\end{figure}

>>>>

\usepackage{showframe}

@@

\begin{figure}[p]
    \centering
    \begin{tikzpicture}
        \matrix {
            \node [anchor=center] {}; &
            \node [anchor=center] {\scriptsize $G(10, x)$}; &
            \node [anchor=center] {\scriptsize $G(14, x)$}; &
            \node [anchor=center] {\scriptsize $G(15, x)$}; &
            \node [anchor=center] {\scriptsize $G(16, x)$}; &
            \node [anchor=center] {\scriptsize $G(20, x)$}; &
            \node [anchor=center] {\scriptsize $G(30, x)$}; &
            \\
            \node [anchor=center] [rotate=90] {\scriptsize Satisfiable?}; &
            \node [anchor=center] {\includegraphics*{gen-graph-induced-satisfiable-10.pdf}}; &
            \node [anchor=center] {\includegraphics*{gen-graph-induced-satisfiable-14.pdf}}; &
            \node [anchor=center] {\includegraphics*{gen-graph-induced-satisfiable-15.pdf}}; &
            \node [anchor=center] {\includegraphics*{gen-graph-induced-satisfiable-16.pdf}}; &
            \node [anchor=center] {\includegraphics*{gen-graph-induced-satisfiable-20.pdf}}; &
            \node [anchor=center] {\includegraphics*{gen-graph-induced-satisfiable-30.pdf}}; &
            \\
            \node [anchor=center] [rotate=90] {\scriptsize Glasgow}; &
            \node [anchor=center] {\includegraphics*{gen-graph-induced-nodes-10.pdf}}; &
            \node [anchor=center] {\includegraphics*{gen-graph-induced-nodes-14.pdf}}; &
            \node [anchor=center] {\includegraphics*{gen-graph-induced-nodes-15.pdf}}; &
            \node [anchor=center] {\includegraphics*{gen-graph-induced-nodes-16.pdf}}; &
            \node [anchor=center] {\includegraphics*{gen-graph-induced-nodes-20.pdf}}; &
            \node [anchor=center] {\includegraphics*{gen-graph-induced-nodes-30.pdf}}; &
            \\
            \node [anchor=center] [rotate=90] {\scriptsize LAD}; &
            \node [anchor=center] {\includegraphics*{gen-graph-lad-induced-nodes-10.pdf}}; &
            \node [anchor=center] {\includegraphics*{gen-graph-lad-induced-nodes-14.pdf}}; &
            \node [anchor=center] {\includegraphics*{gen-graph-lad-induced-nodes-15.pdf}}; &
            \node [anchor=center] {\includegraphics*{gen-graph-lad-induced-nodes-16.pdf}}; &
            \node [anchor=center] {\includegraphics*{gen-graph-lad-induced-nodes-20.pdf}}; &
            \node [anchor=center] {\includegraphics*{gen-graph-lad-induced-nodes-30.pdf}}; &
            \\
            \node [anchor=center] [rotate=90] {\scriptsize VF2}; &
            \node [anchor=center] {\includegraphics*{gen-graph-vf2-induced-nodes-10.pdf}}; &
            \node [anchor=center] {\includegraphics*{gen-graph-vf2-induced-nodes-14.pdf}}; &
            \node [anchor=center] {\includegraphics*{gen-graph-vf2-induced-nodes-15.pdf}}; &
            \node [anchor=center] {\includegraphics*{gen-graph-vf2-induced-nodes-16.pdf}}; &
            \node [anchor=center] {\includegraphics*{gen-graph-vf2-induced-nodes-20.pdf}}; &
            \node [anchor=center] {\includegraphics*{gen-graph-vf2-induced-nodes-30.pdf}}; \\
            \\
            \node [anchor=center] [rotate=90] {\scriptsize Constrainedness}; &
            \node [anchor=center] {\includegraphics*{gen-graph-induced-kappa-10.pdf}}; &
            \node [anchor=center] {\includegraphics*{gen-graph-induced-kappa-14.pdf}}; &
            \node [anchor=center] {\includegraphics*{gen-graph-induced-kappa-15.pdf}}; &
            \node [anchor=center] {\includegraphics*{gen-graph-induced-kappa-16.pdf}}; &
            \node [anchor=center] {\includegraphics*{gen-graph-induced-kappa-20.pdf}}; &
            \node [anchor=center] {\includegraphics*{gen-graph-induced-kappa-30.pdf}}; \\
            \\
            \node [anchor=center] [rotate=90] {\scriptsize Complement?}; &
            \node [anchor=center] {\includegraphics*{gen-graph-induced-which-10.pdf}}; &
            \node [anchor=center] {\includegraphics*{gen-graph-induced-which-14.pdf}}; &
            \node [anchor=center] {\includegraphics*{gen-graph-induced-which-15.pdf}}; &
            \node [anchor=center] {\includegraphics*{gen-graph-induced-which-16.pdf}}; &
            \node [anchor=center] {\includegraphics*{gen-graph-induced-which-20.pdf}}; &
            \node [anchor=center] {\includegraphics*{gen-graph-induced-which-30.pdf}}; \\
        };
    \caption{Behaviour of algorithms on the induced variant, shown in the style
    of \cref{figure:non-induced}. The fifth row plots constrainedness: the darkest region is where
    $\kappa = 1$, and the lighter regions show where the problem is either over-
    or under-constrained. The final row shows when the Glasgow algorithm performs better when given
    the complements of the pattern and target graphs as inputs---the solid lines show the location
of the phase transition, and the dotted lines are $t_d=0.5$ and the $p_d=t_d$ diagonal.}\label{figure:induced}
\end{figure}
